Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-16 cordillera-cycle.tex
Typeset: Fix lon/lat formatting in record table.

\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22~ka after scaling.}
  \label{tab:records}
  {\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (m~a.s.l.) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree} 35' N  % 72.58 (decimal)
             &  37{\degree} 38' W  % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & -5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree} 06' N  % 75.10
             &  42{\degree} 19' W  % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.24 & -6.5  % -26.7098
             & \citet{Andersen.etal.2004} \\

    EPICA    &  75{\degree} 06' S  % 75.1
             & 123{\degree} 21' E  % 123.35
             & 3233
             & \chem{\delta^{18}O}
             & 0.64 & -5.9  % -9.2055
             & \citet{Jouzel.etal.2007} \\

    Vostok   &  78{\degree} 28' S  % 78.8
             & 106{\degree} 50' E  % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.74 & -5.9  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree} 17' N
             & 118{\degree} 23' W
             & -1772
             & \chem{U^{K'}_{37}}
             & 1.61 & -6.1  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree} 00' N
             & 126{\degree} 26' W
             & -3038
             & \chem{U^{K'}_{37}}
             & 1.20 & -6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22~ka after scaling.}
  \label{tab:records}
  {\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (m~a.s.l.) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & -5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree}06$^{\prime}$\,N   % 75.10
             &  42{\degree}19$^{\prime}$\,W   % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.24 & -6.5  % -26.7098
             & \citet{Andersen.etal.2004} \\

    EPICA    &  75{\degree}06$^{\prime}$\,S   % 75.1
             & 123{\degree}21$^{\prime}$\,E   % 123.35
             & 3233
             & \chem{\delta^{18}O}
             & 0.64 & -5.9  % -9.2055
             & \citet{Jouzel.etal.2007} \\

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.74 & -5.9  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree}17$^{\prime}$\,N
             & 118{\degree}23$^{\prime}$\,W
             & -1772
             & \chem{U^{K'}_{37}}
             & 1.61 & -6.1  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & -3038
             & \chem{U^{K'}_{37}}
             & 1.20 & -6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}
